3.3 OLS: OLS: Model Specification Strategies - R Practice

### 2019-10-29 static/r/15-r-practice-rmd.Rmd
Add class 15 content

---
title: "3.3 OLS: Model Specification Strategies - R Practice"
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```

@@

## Question 1

Download and read in (`read_csv`) the data below.

@@

### Part A
Write out the estimated regression equation.

### Part B
What is $\hat{\beta_0}$? What does it mean in the context of our question?

### Part C
What is $\hat{\beta_1}$? What does it mean in the context of our question?

### Part D 
What is the marginal effect of age on amount?

@@

## Question 6
How big would the difference in expected fine be for two drivers, one 18 years old and one 40 years old?

## Question 7
Now run the regression again, controlling for speed (`MPHover`).

@@

## Question 8
Now suppose both the 18 year old and the 40 year old each went 10 MPH over the speed limit. How big would the difference in expected fine be for the two drivers?

## Question 9
How about the difference in expected fine between two 18 year olds, one who went 10 MPH over, and one who went 30 MPH over?

## Question 10
Use the `huxtable` package's `huxreg()` command to make a regression table of your two regressions: the one from question 4, and the one from question 7.

@@

### Part E
Look at your regression table in question 10. What happened to the standard error on `Age`? Why (consider the formula for variation in $\hat{\beta_1})$

@@

### Part B
Look at the regression we ran in Question 4. Consider this the "omitted" regression, where we left out `MPHover`. Does our estimate of the marginal effect of `Age` on `Amount` overstate or understate the *true* marginal effect?

### Part C
Use the "true" model (Question 7), the "omitted" regression (Question 4), and our "auxiliary" regression (Question 11) to identify each of the following parameters that describe our biased estimate of the marginal effect of `Age` on `Amount`:^[See the notation from class 3.2.]
$$\alpha_1=\beta_1+\beta_2\delta1$$

### Part D
From your answer in part C, how large is the omitted variable bias from leaving out `MPHover`?

@@

>>>>

---
title: "3.3 OLS: OLS: Model Specification Strategies - R Practice"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    #theme: 
    toc: true 
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

## Question 1
Download and read in (`read_csv`) the data below.

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part A

Write out the estimated regression equation.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part B

What is $\hat{\beta_0}$? What does it mean in the context of our question?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part C

What is $\hat{\beta_1}$? What does it mean in the context of our question?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part D

What is the marginal effect of age on amount?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 6

How big would the difference in expected fine be for two drivers, one 18 years old and one 40 years old?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 7

Now run the regression again, controlling for speed (`MPHover`).

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 8

Now suppose both the 18 year old and the 40 year old each went 10 MPH over the speed limit. How big would the difference in expected fine be for the two drivers?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 9

How about the difference in expected fine between two 18 year olds, one who went 10 MPH over, and one who went 30 MPH over?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 10

Use the `huxtable` package's `huxreg()` command to make a regression table of your two regressions: the one from question 4, and the one from question 7.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part E
Look at your regression table in question 10. What happened to the standard error on `Age`? Why (consider the formula for variation in $\hat{\beta_1})$
---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part B

Look at the regression we ran in Question 4. Consider this the "omitted" regression, where we left out `MPHover`. Does our estimate of the marginal effect of `Age` on `Amount` overstate or understate the *true* marginal effect?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part C

Use the "true" model (Question 7), the "omitted" regression (Question 4), and our "auxiliary" regression (Question 11) to identify each of the following parameters that describe our biased estimate of the marginal effect of `Age` on `Amount`:^[See the notation from class 3.2.]
$$\alpha_1=\beta_1+\beta_2\delta1$$

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part D

From your answer in part C, how large is the omitted variable bias from leaving out `MPHover`?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---
